XSFACE Analyses

### 2018-01-08 analysis/main_analyses.Rmd
made main r analyses work with new annotations, rendered notebook

---
title: "XSFACE Analyses"
author: "Mike Frank"
date: "July 14, 2016"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

@@

```{r}
mss <- d %>%
  group_by(age.grp, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

@@

```{r}
d <- d %>%
  group_by(subid) %>%
  mutate(face_avg = zoo::rollapply(data = face, 
                                   width = 30*10, # 10s window
                                   FUN = mean, 
                                   align = "right", 
                                   fill = NA, 
                                   na.rm = TRUE))

@@

```{r}
mss <- d %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(posture) & !is.na(orientation)) %>%
  group_by(age.grp, posture, orientation, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

# Naming data

Need some helper functions to merge in namings.

```{r}
source("helper.R")
```

```{r}
namings <- d %>%
  group_by(subid) %>%
  do(summarize.naming(.)) %>%
  left_join(demo %>% select(subid, gender, age.at.test, len))
```

First examine: how many namings do we have, generally?

```{r}
naming_rate <- namings %>%
  group_by(subid, age.grp, age.at.test) %>%
  summarise(num = n(), 
            len = len[1]) %>%
  mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60))

ggplot(naming_rate, 
       aes(x = age.at.test, y = rate)) +
  geom_point() + 
  geom_smooth(span = 1) + 
  ylab("Namings per minute") + 
  xlab("Age (months)") + 
  theme_bw() 
```

Break down by novel and familiar.

```{r}
naming_rate_familiarity <- namings %>%
  group_by(subid, familiarity, age.at.test) %>%
  summarise(num = n(), 
            len = len[1]) %>%
  mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60))

ggplot(naming_rate_familiarity, 
       aes(x = age.at.test, y = rate, col = familiarity)) +
  geom_point() + 
  geom_smooth(span = 1) + 
  ylab("Namings per minute") + 
  xlab("Age (months)") + 
  theme_bw() 
```

Item effects just for fun.

```{r}
namings %>%
  group_by(subid, name, familiarity, age.at.test) %>%
  summarise(num = n(), 
            len = len[1]) %>%
  mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60)) %>%
  ggplot(aes(x = age.at.test, y = rate, col = name)) +
  geom_point() + 
  facet_grid(.~familiarity) + 
  geom_smooth(span = 1) + 
  ylab("Namings per minute") + 
  xlab("Age (months)") + 
  theme_bw() 
```

# Namings and face detections

## Are there more faces during naming instances?

## Are there more faces before or after naming instances?

```{r}
#   sb <- ddply(d,~subid, summarize.naming, window=c(-3,0))
#   sa <- ddply(d,~subid, summarize.naming, window=c(0,3))
#   sb$window <- "before"
#   sa$window <- "after"
#   s <- rbind(sb,sa)
#   s$window <- factor(s$window)
#   
# #   d <- subset(d,!is.na(time))
# #   s <- ddply(d,~subid, summarize.naming, window=c(-3,3))
#   
#   s$first.instance <- s$naming.instance == 1
#   s$log.instance <- round(log10(s$naming.instance)*4)/4
#   s$binned.instance <- 10^(round(log10(s$naming.instance)*4)/4)
#   s$face.logical <- s$face != 0
#   
#   ## try plotting individuals
#   mss <- ddply(s,~subid+age.grp+window,summarise,
#                face = na.mean(face))
```

```{r}
  # qplot(age.grp,face,colour=window,
  #       xlab="Age (Months)",ylab="Proportion faces detected in window",
  #       data=mss,geom=c("point")) + 
  #   scale_x_continuous(breaks=c(8,12,16)) +
  #   geom_smooth()
```

## How do face detections change with sequence of naming instances?

```{r}
ms <- namings %>%
  group_by(age.grp, subid, naming.instance, familiarity, name) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp, naming.instance, familiarity) %>%
  multi_boot_standard(col = "face", na.rm = TRUE)
```

```{r}
ggplot(ms, 
       aes(x = naming.instance, y = mean, col = familiarity)) +
  geom_point() + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_smooth(se = FALSE) + 
  facet_grid(~age.grp) + 
  xlim(c(0,20)) + 
  scale_color_solarized() + 
  theme_bw()

```

```{r}

#   ## now calculate differences from base rate
#   n <- ddply(s,~subid+age.grp,summarise,
#              face = na.mean(face))
#   
#   n$br <- ddply(d,~subid+age.grp,summarise,
#               face=na.mean(face))$face
#   
#   n$br.diff <- n$face - n$br
#   
# #   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3)
#   qplot(age.grp,br.diff,position=position_jitter(.2),
#         data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") + 
#     scale_x_continuous(breaks=c(8,12,16,20)) +
#     geom_abline(slope=0,intercept=0,lty=2) + 
#     stat_summary(fun.data="mean_cl_boot",color="red")
# #   dev.off()
```

# CDIs, namings, and face detections

```{r}
cdi_namings <- left_join(naming_rate, cdis)

qplot(comprehension, facets= .~ age.grp, data = cdi_namings) + 
  theme_bw()

qplot(production, facets= .~ age.grp, data = cdi_namings) + 
  theme_bw()

```

## CDIs and namings

Just out of curiousity, are there any major differences in terms of CDIs by naming rate? (Would help to establish the validity of the naming rate analyses).

```{r}
ggplot(cdi_namings, 
       aes(x = rate, y = comprehension)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  facet_grid(.~age.grp) + 
  xlab("Namings per minute") + 
  ylab("CDI Summed Comprehension Vocabulary") + 
  theme_bw()
```

```{r}
cdis <- read_csv("../data/cdis/cdi_summary.csv")
left_join(naming_rate, cdis) %>%
  ggplot(aes(x = rate, y = production)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  facet_grid(.~age.grp) + 
  xlab("Namings per minute") + 
  ylab("CDI Summed Production Vocabulary") + 
  theme_bw()
```

>>>>

---
title: "XSFACE Analyses"
author: "Mike Frank, continued Bria Long"
date: "July 14, 2016; January 8, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

@@

```{r}
d$face_num<-as.numeric(d$is_face=="TRUE")

mss <- d %>%
  group_by(age.grp, subid) %>%
  filter(!is.na(face_num)) %>% # filter out NA values
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  filter(!is.na(face_num)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face_num)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

@@

```{r}
d <- d %>%
  group_by(subid) %>%
  filter(!is.na(face_num)) %>%
  mutate(face_avg = zoo::rollapply(data = face_num, 
                                   width = 30*10, # 10s window
                                   FUN = mean, 
                                   align = "right", 
                                   fill = NA, 
                                   na.rm = TRUE))

@@

```{r}
mss <- d %>%
  filter(!is.na(posture)) %>%
  filter(!is.na(face_num)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(orientation)) %>%
  filter(!is.na(face_num)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(posture) & !is.na(orientation) & !is.na(face_num)) %>%
  group_by(age.grp, posture, orientation, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

<!-- # Naming data -->

<!-- Need some helper functions to merge in namings.  -->

<!-- ```{r} -->
<!-- source("helper.R") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- namings <- d %>% -->
<!--   group_by(subid) %>% -->
<!--   do(summarize.naming(.)) %>% -->
<!--   left_join(demo %>% select(subid, gender, age.at.test, len)) -->
<!-- ``` -->

<!-- First examine: how many namings do we have, generally?  -->

<!-- ```{r} -->
<!-- naming_rate <- namings %>% -->
<!--   group_by(subid, age.grp, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60))  -->

<!-- ggplot(naming_rate,  -->
<!--        aes(x = age.at.test, y = rate)) + -->
<!--   geom_point() +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- Break down by novel and familiar.  -->

<!-- ```{r} -->
<!-- naming_rate_familiarity <- namings %>% -->
<!--   group_by(subid, familiarity, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60)) -->

<!-- ggplot(naming_rate_familiarity,  -->
<!--        aes(x = age.at.test, y = rate, col = familiarity)) + -->
<!--   geom_point() +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- Item effects just for fun.  -->

<!-- ```{r} -->
<!-- namings %>% -->
<!--   group_by(subid, name, familiarity, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60)) %>% -->
<!--   ggplot(aes(x = age.at.test, y = rate, col = name)) + -->
<!--   geom_point() +  -->
<!--   facet_grid(.~familiarity) +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- # Namings and face detections -->

<!-- ## Are there more faces during naming instances?  -->

<!-- ## Are there more faces before or after naming instances?  -->

<!-- ```{r} -->
<!-- #   sb <- ddply(d,~subid, summarize.naming, window=c(-3,0)) -->
<!-- #   sa <- ddply(d,~subid, summarize.naming, window=c(0,3)) -->
<!-- #   sb$window <- "before" -->
<!-- #   sa$window <- "after" -->
<!-- #   s <- rbind(sb,sa) -->
<!-- #   s$window <- factor(s$window) -->
<!-- #    -->
<!-- # #   d <- subset(d,!is.na(time)) -->
<!-- # #   s <- ddply(d,~subid, summarize.naming, window=c(-3,3)) -->
<!-- #    -->
<!-- #   s$first.instance <- s$naming.instance == 1 -->
<!-- #   s$log.instance <- round(log10(s$naming.instance)*4)/4 -->
<!-- #   s$binned.instance <- 10^(round(log10(s$naming.instance)*4)/4) -->
<!-- #   s$face.logical <- s$face != 0 -->
<!-- #    -->
<!-- #   ## try plotting individuals -->
<!-- #   mss <- ddply(s,~subid+age.grp+window,summarise, -->
<!-- #                face = na.mean(face)) -->
<!-- ```   -->

<!-- ```{r} -->
<!--   # qplot(age.grp,face,colour=window, -->
<!--   #       xlab="Age (Months)",ylab="Proportion faces detected in window", -->
<!--   #       data=mss,geom=c("point")) +  -->
<!--   #   scale_x_continuous(breaks=c(8,12,16)) + -->
<!--   #   geom_smooth() -->
<!-- ``` -->

<!-- ## How do face detections change with sequence of naming instances? -->

<!-- ```{r} -->
<!-- ms <- namings %>% -->
<!--   group_by(age.grp, subid, naming.instance, familiarity, name) %>% -->
<!--   summarise(face = mean(face)) %>% -->
<!--   group_by(age.grp, naming.instance, familiarity) %>% -->
<!--   multi_boot_standard(col = "face", na.rm = TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(ms,  -->
<!--        aes(x = naming.instance, y = mean, col = familiarity)) + -->
<!--   geom_point() +  -->
<!--   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +  -->
<!--   geom_smooth(se = FALSE) +  -->
<!--   facet_grid(~age.grp) +  -->
<!--   xlim(c(0,20)) +  -->
<!--   scale_color_solarized() +  -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #   ## now calculate differences from base rate -->
<!-- #   n <- ddply(s,~subid+age.grp,summarise, -->
<!-- #              face = na.mean(face)) -->
<!-- #    -->
<!-- #   n$br <- ddply(d,~subid+age.grp,summarise, -->
<!-- #               face=na.mean(face))$face -->
<!-- #    -->
<!-- #   n$br.diff <- n$face - n$br -->
<!-- #    -->
<!-- # #   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3) -->
<!-- #   qplot(age.grp,br.diff,position=position_jitter(.2), -->
<!-- #         data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") +  -->
<!-- #     scale_x_continuous(breaks=c(8,12,16,20)) + -->
<!-- #     geom_abline(slope=0,intercept=0,lty=2) +  -->
<!-- #     stat_summary(fun.data="mean_cl_boot",color="red") -->
<!-- # #   dev.off() -->
<!-- ``` -->

<!-- # CDIs, namings, and face detections -->

<!-- ```{r} -->
<!-- cdi_namings <- left_join(naming_rate, cdis) -->

<!-- qplot(comprehension, facets= .~ age.grp, data = cdi_namings) +  -->
<!--   theme_bw() -->

<!-- qplot(production, facets= .~ age.grp, data = cdi_namings) +  -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ## CDIs and namings -->

<!-- Just out of curiousity, are there any major differences in terms of CDIs by naming rate? (Would help to establish the validity of the naming rate analyses).  -->

<!-- ```{r} -->
<!-- ggplot(cdi_namings,  -->
<!--        aes(x = rate, y = comprehension)) +  -->
<!--   geom_point() +  -->
<!--   geom_smooth(method = "lm", se = FALSE) +  -->
<!--   facet_grid(.~age.grp) +  -->
<!--   xlab("Namings per minute") +  -->
<!--   ylab("CDI Summed Comprehension Vocabulary") +  -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- cdis <- read_csv("../data/cdis/cdi_summary.csv") -->
<!-- left_join(naming_rate, cdis) %>% -->
<!--   ggplot(aes(x = rate, y = production)) +  -->
<!--   geom_point() +  -->
<!--   geom_smooth(method = "lm", se = FALSE) +  -->
<!--   facet_grid(.~age.grp) +  -->
<!--   xlab("Namings per minute") +  -->
<!--   ylab("CDI Summed Production Vocabulary") +  -->
<!--   theme_bw() -->
<!-- ``` -->

### 2018-01-08 analysis/main_analyses_bll.Rmd
made main r analyses work with new annotations, rendered notebook

```{r}
d$face_num<-as.numeric(d$is_face=="TRUE")

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  filter(!is.na(face_num)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face_num)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

>>>>

```{r}
d$face_num<-as.numeric(d$is_face=="True")

@@

```{r, d}

mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  filter(!is.na(face_num)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face_num)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))
